%-------------------------
% Resume in Latex
% Author : Kyle Hovey
% Template Creator : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,8pt]{article}

\renewcommand{\familydefault}{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://kylehovey.github.io}{\Large Kyle Hovey}} & Email : \href{mailto:khoveyc@gmail.com}{khoveyc@gmail.com}\\
	\href{http://kylehovey.github.io}{kylehovey.github.io} & Mobile : +1-209-768-7550 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Utah State University}{Logan, UT}
      {Computational Mathematics (BS);  GPA:  3.88; Magna Cum Laude}{Aug 2015 -- Dec 2018}
    \resumeSubheading
      {Cuesta College}{San Luis Obispo, CA}
      {Three semesters to transfer;  GPA: 3.95}{Jan 2014 -- May 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Brilliant Worldwide}{San Francisco, CA}
      {Senior Software Engineer I}{Oct 2021 -- Present}
      \resumeItemListStart
      \resumeItem{Authoring Team}
      {Collaborated on a versatile lesson editor that enables producers to create world-class interactive STEM lessons.}
      \resumeItem{Interactives Experience Pod}
      {Developed and planned interactive features to enrich learner experience, including gamification of learning with Leagues.}
      \resumeItem{Web Platform and Infrastructure - Tech Lead}
      {Served as Tech Lead on an ambitious project to rewrite Brilliant's frontend codebase with React/GraphQL/NextJS.}
      \resumeItemListEnd

    \resumeSubheading
      {Atomic Jolt}{Logan, UT}
      {Software Engineer}{Jun 2018 -- Oct 2021}
      \resumeItemListStart
      \resumeItem{Learnosity Connector}
      {Contributed to the Learnosity Connector project which enables teachers to author course content in Canvas via the popular Learnosity service.}
      \resumeItem{Socialize}
      {Developed new elements of Atomic Jolt's Socialize platform for polls and discussions between students.}
      \resumeItem{Waymaker}
      {Collaborated with Lumen Learning on the Waymaker project and developed educational workflow software.}
      \resumeItem{Atomic Insight}
      {Led the Insight project to replace Canvas Analytics with a novel LTI stack written in Go+React to deliver customized metrics into Canvas Courses}
      \resumeItemListEnd

    \resumeSubheading
      {USU Power Electronics Laboratory}{Logan, UT}
      {Software Engineer / Research Assistant}{Jan 2016 -- Jun 2018}
      \resumeItemListStart
        \resumeItem{Square One -- Altium Library Management System}
        {Created a system using Node$+$Express for mass-submitting tickets for new parts to be added to our in-house Altium Database and verified by librarians.}
        \resumeItem{CAN Data Graphing Utility}
        {Created a application for generating and sharing graphs of terabytes of data accrued in the AMPED battery life extension project.}
      \resumeItem{Graphic Design}
        {Designed all the banners and window decals around our facilities in Logan, UT. Utilized a unified color palette for all the facets of our organization.}
      \resumeItemListEnd

    \resumeSubheading
      {USU GAS Lab}{Logan, UT}
      {Volunteer Software Engineer}{Apr 2017 -- Dec 2018}
      \resumeItemListStart
      \resumeItem{Cubium Software Project}
      {A volunteer of the Get-Away-Special small-satellite program at Utah State University. Developed open source subscription-based plug and play software for small satellite application as well as new hardware that will empower individuals to deploy experiments on a budget.}
      \resumeItemListEnd

    \resumeSubheading
      {West Coast Astronomical Society}{Santa Margarita, CA}
      {Head of Mechatronics}{Jun 2014 -- Jan 2015}
      \resumeItemListStart
        \resumeItem{Telescope Automation}
        {Took charge of automating the hardware of a Meade 10`` telescope to more accurately detect the positions of binary star systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{USU - Magna Cum Laude}
    {Graduated Magna Cum Laude in the Computational Mathematics program at USU}
    \resumeSubItem{USU Hackathon (2016 -- 2018)}
    {Took first place three years in a row at the Utah State University intercollegiate hackathon}
    \resumeSubItem{Cuesta College FBSA (2015)}
    {Awarded the Frank Brown Science Award for outstanding academic achievement.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{8-Bit Spaghetti}
    {Designed and built 8-bit processor using TTL. Helped many students around the world build versions of the design.}
    \resumeSubItem{Dream Cloak LED Display}
    {Designed and built a 15x30 24-bit wearable RGB LED display and a web app to control it wirelessly, all in five days.}
    \resumeSubItem{Automata Research}
    {Developed novel approach to classifying all Life-Like Cellular Automata by a similarity metric.}
    \resumeSubItem{Health Research}
    {Designed and built personal health analysis applications (ECG/Apple Health) for insight and knowledge into their own health.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: TS/JS, CSS/Sass, Python, C++, Ruby, Julia, Go, SQL, Elm, Haskell, LISP, Bash, LaTeX}
    }
    \item{
      \textbf{Technologies}{: React, NextJS, GraphQL, Svelte, Node.js, Rails, Django, Numpy, Postgres, WebSocket}
    }
    \item{
      \textbf{Operating Systems}{: MacOS, Arch, Ubuntu/Debian, CentOS, Windows}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
