%-------------------------
% Resume in Latex
% Author : Val Hovey
% Template Creator : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,8pt]{article}

\renewcommand{\familydefault}{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 & \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://valhovey.github.io}{\Large Val Hovey}} & Email : \href{mailto:khoveyc@gmail.com}{khoveyc@gmail.com}\\
	\href{http://valhovey.github.io}{valhovey.github.io} & Mobile : +1-209-768-7550 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Utah State University}{Logan, UT}
      {Computational Mathematics (BS);  GPA:  3.88; Magna Cum Laude}{Aug 2015 -- Dec 2018}
    \resumeSubheading
      {Cuesta College}{San Luis Obispo, CA}
      {Three semesters to transfer;  GPA: 3.95}{Jan 2014 -- May 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mercury Technologies}{San Francisco, CA}
      {Senior Software Engineer II (IC4)}{May 2023 -- Present}
      \resumeItemListStart
      \resumeItem{Automatic Receipts Matching}
      {Authored spec and implemented automatic receipts matching at Mercury, used by thousands of orgs and over \$100M in transactions with an average match rate of 90\%}
      \resumeItem{Departments}
      {Authored spec and built BE framework for Departments abstraction in collaboration between multiple teams}
      \resumeItem{Automatic Categorization}
      {Authored spec and implemented automatic category to GL code mapping with third party syncing used by thousands of organizations}
      \resumeItem{Transaction Enrichment}
      {Implemented transaction categorization and enrichment backends}
      \resumeItem{Mentorship}
      {Collaborated on technical interview rubrics and mentored new hires on Haskell}
      \resumeItemListEnd

    \resumeSubheading
      {Brilliant Worldwide}{San Francisco, CA}
      {Senior Software Engineer}{Oct 2021 -- May 2023}
      \resumeItemListStart
      \resumeItem{Web Platform and Infrastructure - Tech Lead}
      {Served as Tech Lead on an ambitious project to rewrite Brilliant's frontend codebase with React/GraphQL/NextJS.}
      \resumeItem{Interactives Experience Pod}
      {Developed and planned interactive features to enrich learner experience, including gamification of learning with Leagues.}
      \resumeItem{Authoring Team}
      {Collaborated on a versatile lesson editor that enables producers to create world-class interactive STEM lessons.}
      \resumeItemListEnd

    \resumeSubheading
      {Atomic Jolt}{Logan, UT}
      {Software Engineer}{Jun 2018 -- Oct 2021}
      \resumeItemListStart
      \resumeItem{Learnosity Connector}
      {Contributed to the Learnosity Connector project which enables teachers to author course content in Canvas via the popular Learnosity service.}
      \resumeItem{Socialize}
      {Developed new elements of Atomic Jolt's Socialize platform for polls and discussions between students.}
      \resumeItem{Waymaker}
      {Collaborated with Lumen Learning on the Waymaker project and developed educational workflow software.}
      \resumeItem{Atomic Insight}
      {Led the Insight project to replace Canvas Analytics with a novel LTI stack written in Go+React to deliver customized metrics into Canvas Courses}
      \resumeItemListEnd

    \resumeSubheading
      {USU Power Electronics Laboratory}{Logan, UT}
      {Software Engineer / Research Assistant}{Jan 2016 -- Jun 2018}
      \resumeItemListStart
        \resumeItem{Square One -- Altium Library Management System}
        {Created a system using Node$+$Express for mass-submitting tickets for new parts to be added to our in-house Altium Database and verified by librarians.}
        \resumeItem{CAN Data Graphing Utility}
        {Created a application for generating and sharing graphs of terabytes of data accrued in the AMPED battery life extension project.}
        \resumeItem{Battery Embedded Development}
        {Contributed to battery firmware updates to publish sensor data on a CAN bus}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{USU - Magna Cum Laude}
    {Graduated Magna Cum Laude in the Computational Mathematics program at USU}
    \resumeSubItem{USU Hackathon (2016 -- 2018)}
    {Took first place three years in a row at the Utah State University intercollegiate hackathon}
    \resumeSubItem{Cuesta College FBSA (2015)}
    {Awarded the Frank Brown Science Award for outstanding academic achievement.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{8-Bit Spaghetti}
    {Designed and built 8-bit processor using TTL. Helped many students around the world build versions of the design.}
    \resumeSubItem{AQI IoT Devices}
    {Developed multiple air quality IoT devices including a portable MQTT enabled PM2.5/CO2/NOX/VOC/Temp/Humidity device on ESP32}
    \resumeSubItem{RGB Fairy Lights}
    {Developed and built individually addressable RGB fairy lights controllable over Home Assistant via MQTT}
    \resumeSubItem{Dream Cloak LED Display}
    {Designed and built a 15x30 24-bit wearable RGB LED display and a web app to control it wirelessly, all in five days.}
    \resumeSubItem{Automata Research}
    {Developed novel approach to classifying all Life-Like Cellular Automata by a similarity metric.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
        \textbf{Languages}{: Haskell, C++20, Python, Typescript, Ruby, SQL, Bash, LaTeX}
    }
    \item{
        \textbf{Technologies}{: Postgres, Yesod, NextJS, Node, React, Svelte, Arduino, ESP32}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
